---
title: "Integrated ensemble"
output:
  word_document: default
  html_document: default
date: "2024-11-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = FALSE)
```


## Integrated ensemble
### Function CM to compute F1 scores for both corpora
```{r cm2-fanction}
suppressMessages(suppressWarnings(library(caret)))
#install.packages("kableExtra") 
suppressMessages(suppressWarnings(library(kableExtra)))

col.lab<-c("Recall_mean","Recall_sd","Preci_mean","Preci_sd","F1_mean","F1_sd")
B.lab<-c("T","A","AW","De","S")

cm2<-function(X){
RES<-matrix(0,10,10)
X<-as.matrix(X)
for(i in 1:100)
{
res<-sort.list(X[i,-1],decreasing = TRUE)[1]
RES[X[i,1]+1,res]<-RES[X[i,1]+1,res]+1
}
a<-apply(confusionMatrix(RES,mode="prec_recall")$byClass[,c(6,5,7)],2,mean)
b<-apply(confusionMatrix(RES,mode="prec_recall")$byClass[,c(6,5,7)],2,sd)
res<-data.frame(rbind(a,b))
#res
res_vector<-c(res[1,1],res[2,1],res[1,2],res[2,2],res[1,3,],res[2,3])
names(res_vector)<-col.lab
list(vec=res_vector,matri=res)
}

```

### Read BERTs test results (probability vectors)
```{r result1}
corpusA<-list()
corpusB<-list()

suppressMessages(suppressWarnings(library(readxl)))
path1<-"C:/ensemble/CorpusA_BERT_Test_Results.xlsx"
BERT.A<-list()
for(i in 1:5)
  BERT.A[[i]] <- suppressMessages(suppressWarnings(
    read_excel(path1, sheet = i,col_names = FALSE)))

path2<-"C:/ensemble/CorpusB_BERT_Test_Results.xlsx"
BERT.B<-list()
for(i in 1:5)
  BERT.B[[i]] <- suppressMessages(suppressWarnings(
    read_excel(path2, sheet = i,col_names = FALSE)))
```

### Compute BERTs scores
```{r Compute BERTs scores}
suppressMessages(suppressWarnings(library(knitr)))
# Calculating BERT scores for Corpus A
singBERT.A<-numeric()
for(i in 1:5)
  singBERT.A<-rbind(singBERT.A,cm2(BERT.A[[i]])[[1]])

singBERT.A<-data.frame(lab=B.lab,singBERT.A)

BERT.lab<-c("TohokuB","AozoraB","AozoraWikiB","DeBERTa","StockMarkB")
rownames(singBERT.A)<-BERT.lab
colnames(singBERT.A)<-c("lab",col.lab)
write.csv(singBERT.A,"C:/ensemble/singBERT.A.csv")
corpusA[[1]]<-singBERT.A[,6]

table2A<-singBERT.A;
table2A[,-1]<-round(table2A[,-1],3)
kable(table2A, format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")


# Calculating BERT scores for Corpus B
path2<-"C:/ensemble/CorpusB_BERT_Test_Results.xlsx"
BERT.B<-list()
for(i in 1:5) 
  BERT.B[[i]] <- suppressMessages(read_excel(path2, sheet = i,col_names = FALSE))

singBERT.B<-numeric()
for(i in 1:5)
  singBERT.B<-rbind(singBERT.B,cm2(BERT.B[[i]])[[1]])

singBERT.B<-as.matrix(singBERT.B)
colnames(singBERT.B)<-col.lab
rownames(singBERT.B)<-BERT.lab
singBERT.B<-data.frame(lab=B.lab,singBERT.B)
write.csv(singBERT.B,"C:/ensemble/singBERT.B.csv")

table2B<-singBERT.B;
table2B[,-1]<-round(table2B[,-1],3)
kable(table2B, format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
corpusB[[1]]<-singBERT.B[,6]
table2<-data.frame(rbind(table2A,table2B))
write.csv(table2,"C:/ensemble/table2.csv")

#corpusB[[1]]
```

### Ensemble BERTs functions for both corpora
### Ensemble of two BERTs
```{r Ensemble 2}
col.lab<-c("Recall_mean","Recall_sd","Preci_mean","Preci_sd","F1_mean","F1_sd")
B.lab<-c("T","A","AW","De","S")

ensemb2<-function(BB,w){
#BB is the test result list data.
#w is the weight vector .
#ensemble of any two BERTs
  
B.lab<-c("T","A","AW","De","S")
comb2<-combn(1:5, 2)
string=c()
resu=numeric()
for(i in 1:ncol(comb2)){
J<-comb2[1,i]
K<-comb2[2,i]
X<-BB[[J]]; X[,-1]<-X[,-1]*w[1]+w[2]*BB[[K]][,-1]

#Calculate F1 values, etc. from contingency table
string=c(string,paste("{",B.lab[J],",",B.lab[K],"}"))
resu<-rbind(resu,cm2(X)[[1]])
  }
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=string,resu)
resu
}
```

### Ensemble of three BERTs
```{r Ensemb3}
# Ensemble of three BERT results
ensemb3<-function(BB,w){
comb3<-combn(1:5, 3)
string=c()
resu=numeric()

for(i in 1:ncol(comb3)){
J<-comb3[1,i]
K<-comb3[2,i]
L<-comb3[3,i]
X<-BB[[J]]
X[,-1]<-X[,-1]*w[J]+w[K]*BB[[K]][,-1]+w[L]*BB[[L]][,-1]

string=c(string,paste("{",B.lab[J],",",B.lab[K],",",B.lab[L],"}"))
resu<-rbind(resu,cm2(X)[[1]])
}
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=string,resu)
resu
}
```

### Ensemble of four annd five BERTs
```{r Ensemb 4-5}
# Ensemble of 4 and 5 BERT results
ensemb4<-function(BB,w){
string=c()
resu=numeric()

comb4<-combn(1:5, 4)
for(i in 1:ncol(comb4)){
J<-comb4[1,i]
K<-comb4[2,i]
L<-comb4[3,i]
G<-comb4[4,i]
X<-BB[[J]];
X[,-1]<-X[,-1]*w[J]+w[K]*BB[[K]][,-1]+BB[[L]][,-1]*w[L]+w[G]*BB[[G]][,-1]
string=c(string,paste("{",B.lab[J],",",B.lab[K],",",B.lab[L],",",B.lab[G],"}"))
resu<-rbind(resu,cm2(X)[[1]])
}

#Ensemble of five BERT results
X<-BB[[1]];X[,-1]<-X[,-1]*w[1]+w[2]*BB[[2]][,-1]+BB[[3]][,-1]*w[3]+w[4]*BB[[4]][,-1]+w[5]*BB[[5]][,-1]

resu<-rbind(resu,cm2(X)[[1]])
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=c(string,"{T,A,AW,De,S}"),resu)
resu
}

```
### Compute ensemble results for corpus A

```{r Ensemb  Corpus A}
# Calculate the results of the corpus A ensemble
w<-c(1,1,1,1,1)
resu.A2<-ensemb2(BERT.A, w)
resu.A3<-ensemb3(BERT.A, w)
resu.A4<-ensemb4(BERT.A, w)
ensemBERT.A<-rbind(resu.A2,resu.A3,resu.A4)
temp<-sort.list(ensemBERT.A[,6],decreasing=TRUE)
ensemBERT.A<-data.frame(ensemBERT.A[temp,])
rownames(ensemBERT.A)<-1:dim(ensemBERT.A)[1]
write.csv(ensemBERT.A,"C:/ensemble/ensemBERT.A.csv")
corpusA[[2]] <- ensemBERT.A[,6]
kable(head(ensemBERT.A),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

# Calculate the results of the corpus A weighted ensemble
w<-singBERT.A[,6]
resu.A2<-ensemb2(BERT.A, w)
resu.A3<-ensemb3(BERT.A, w)
resu.A4<-ensemb4(BERT.A, w)
ensemBERT.A.W<-rbind(resu.A2,resu.A3,resu.A4)
temp<-sort.list(ensemBERT.A.W[,6],decreasing=TRUE)
ensemBERT.A.W<-data.frame(ensemBERT.A.W[temp,])
rownames(ensemBERT.A.W)<-1:dim(ensemBERT.A.W)[1]
write.csv(ensemBERT.A.W,"C:/ensemble/ensemBERT.A.W.csv")

corpusA[[3]] <- ensemBERT.A.W[,6]

ensemBERT.A[,6]
```

### Compute ensemble results for corpus B
```{r Ensemb  Corpus B}
# Calculate the results of the corpus A ensemble
w<-c(1,1,1,1,1)
resu.B2<-ensemb2(BERT.B,w)
resu.B3<-ensemb3(BERT.B,w)
resu.B4<-ensemb4(BERT.B,w)
ensemBERT.B<-rbind(resu.B2,resu.B3,resu.B4)

temp<-sort.list(ensemBERT.B[,6],decreasing=TRUE)
ensemBERT.B<-data.frame(ensemBERT.B[temp,])
rownames(ensemBERT.B)<-1:dim(ensemBERT.B)[1]
write.csv(ensemBERT.B,"C:/ensemble/ensemBERT.B.csv")
corpusB[[2]]<-ensemBERT.B[,6]
kable(head(ensemBERT.B),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

# Calculate the results of the corpus B weighted ensemble
w<-singBERT.B[,6]     
resu.B2<-ensemb2(BERT.B,w)
resu.B3<-ensemb3(BERT.B,w)
resu.B4<-ensemb4(BERT.B,w)
ensemBERT.B.W<-rbind(resu.B2,resu.B3,resu.B4)
temp<-sort.list(ensemBERT.B.W[,6],decreasing=TRUE)
ensemBERT.B.W<-data.frame(ensemBERT.B.W[temp,])
rownames(ensemBERT.B.W)<-1:dim(ensemBERT.B)[1]
write.csv(ensemBERT.B.W,"C:/ensemble/ensemBERT.B.W.csv")

corpusB[[3]]<-ensemBERT.B.W[,6]
ensemBERT.B.W[,6]
```

### Draw the box plot of BERT's and ensemble F1 scores
```{r Drawing box-plot}
# Drawing the resulting box plot
par(mfrow=c(1,2), cex.lab = 0.7, cex.axis = 0.7) 
lab=factor(c(rep("sin",each=5),rep("ens",each=26),rep("wens",each=26)),levels = c("sin", "ens","wens"))
col<-c("lightblue","gold1","pink")
#Boxplot of F1 values for Corpus A
F1<-c(singBERT.A[,6],ensemBERT.A[,6],ensemBERT.A.W[,6])
BERT.A.resu<-data.frame(lab=lab,F1=F1)
boxplot(F1 ~ lab, data = BERT.A.resu,col=col,ylab="",xlab="");grid()
legend("bottomright", legend = c("sin: Single BERT", "en: Ensemble BERTs","wens: Wighted Ensemble BERTs"), fill = col, cex = 0.6)
#Boxplot of F1 values for Corpus B
F1<-c(singBERT.B[,6],ensemBERT.B[,6],ensemBERT.B.W[,6])
BERT.B.resu<-data.frame(lab=lab,F1=F1)
boxplot(F1 ~ lab, data = BERT.B.resu,col=col,ylab="",xlab="");grid()
legend("bottomright", legend = c("sin: Single BERT", "en: Ensemble BERTs","wens: Wighted Ensemble BERTs"), fill = col, cex = 0.6)

```


### Load Features & Classifiers test results
```{r Load Features & Classifiers}
library(readxl)
path3<-"C:/ensemble/CorpusA_Feature&Classifiers_Test_Results.xlsx"
AdaRF.A<-list()
#Ada.Char,Ada.Token, Ada.Pattern,RF.Char,RF.Token, RF.Pattern
for(i in 1:6)
AdaRF.A[[i]] <- suppressMessages(read_excel(path3, sheet = i,col_names = FALSE))

path4<-"C:/ensemble/CorpusB_Feature&Classifiers_Test_Results.xlsx"
AdaRF.B<-list()
#Ada.Char,Ada.Token, Ada.Pattern,RF.Char,RF.Token, RF.Pattern
for(i in 1:6)
  AdaRF.B[[i]] <- suppressMessages(read_excel(path4, sheet = i,col_names = FALSE))
```

## Compute single F & C scores for Corpus A

```{r}
resu<-numeric()
for(i in 1:6) resu<-rbind(resu,cm2(AdaRF.A[[i]])[[1]])

##Table type the results of corpus A
resu<-data.frame(resu)
colnames(resu)<-col.lab
F.lab<-c("Ada.Char","Ada.Token","Ada.Pattern","RF.Char","RF.Token","RF.Pattern")
FeaClas.A<-data.frame(lab=F.lab,resu)
corpusA[[4]]<-FeaClas.A[,6]
write.csv(FeaClas.A,"C:/ensemble/FeaClas.A.csv")
table3A<-FeaClas.A
table3A[,-1]<-round(FeaClas.A[,-1],3)
kable(table3A,format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
```

## Compute single F & C scores for Corpus B
```{r for Corpus B}
##Corpus B
resu<-numeric()
for(i in 1:6) resu<-rbind(resu,cm2(AdaRF.B[[i]])[[1]])

resu<-data.frame(resu)
colnames(resu)<-col.lab
FeaClas.B<-data.frame(lab=F.lab,resu)
write.csv(FeaClas.B,"C:/ensemble/FeaClas.B.csv")
corpusB[[4]]<-FeaClas.B[,6]

table3B<-FeaClas.B
table3B[,-1]<-round(FeaClas.B[,-1],3)
kable(table3B,format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
table3<-data.frame(rbind(table3A,table3B))
write.csv(table3,"C:/ensemble/table3.csv")

```
## Ensemble of F & C
### Function of ensemble of two F & C
```{r ensemble two C & F }
#Two ensemble functions
FEnsemb2<-function(FE,w){
comb2<-combn(1:6,2 )
string=c()
resu=numeric()

for(i in 1:ncol(comb2)){
J<-comb2[1,i]
K<-comb2[2,i]
X<-FE[[J]];X[,-1]<-w[J]*X[,-1]+w[K]*FE[[K]][,-1]
string=c(string,paste("{",J,",",K,"}"))
resu<-rbind(resu,cm2(X)[[1]])
  }
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=string,resu)
resu
}

```
### Function of ensemble of three F & C
```{r ensemble CF 3}
FEnsemb3<-function(FE,w){
res<-list()
string=c()
resu=numeric()
comb3<-combn(1:6, 3)
for(i in 1:ncol(comb3)){
J<-comb3[1,i]
K<-comb3[2,i]
L<-comb3[3,i]
X<-FE[[J]]
X[,-1]<-w[J]*X[,-1]+w[K]*FE[[K]][,-1]+w[L]*FE[[L]][,-1]

string=c(string,paste("{",J,",",K,",",L,"}"))
resu<-rbind(resu,cm2(X)[[1]])
  }
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=string,resu)
resu
}

```
### Function of ensemble of four F & C
```{r ensemble CF 4}
FEnsemb4<-function(FE,w){
res<-list()
string=c()
resu=numeric()
comb4<-combn(1:6, 4)
res<-list()
for(i in 1:ncol(comb4)){
  J<-comb4[1,i]
  K<-comb4[2,i]
  L<-comb4[3,i]
  G<-comb4[4,i]
  X<-FE[[J]]
  X[,-1]<-w[J]*X[,-1]+w[K]*FE[[K]][,-1]+w[L]*FE[[L]][,-1]+w[G]*FE[[G]][,-1]

string=c(string,paste("{",J,",",K,",",L,",",G,"}"))
resu<-rbind(resu,cm2(X)[[1]])
  }
resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=string,resu)
resu
}

```
### Function of ensemble of five and six F & C
```{r ensemble CF 5,6}
FEnsemb5<-function(FE,w){
string=c()
resu=numeric()
comb5<-combn(1:6, 5)

for(i in 1:ncol(comb5)){
J<-comb5[1,i]; K<-comb5[2,i];L<-comb5[3,i]
G<-comb5[4,i]; F<-comb5[5,i];
X<-FE[[J]]
X[,-1]<-w[J]*X[,-1]+w[K]*FE[[K]][,-1]+w[L]*FE[[L]][,-1]+w[G]*FE[[G]][,-1]+w[F]*FE[[F]][,-1]

string=c(string,paste("{",J,",",K,",",L,",",G,",",F,"}"))
resu<-rbind(resu,cm2(X)[[1]])
}
## ensemble six F & C
X<-FE[[1]]
X[,-1]<-w[1]*X[,-1]+w[2]*FE[[2]][,-1]+w[3]*FE[[3]][,-1]+w[4]*FE[[4]][,-1]+
        w[5]*FE[[5]][,-1]+w[6]*FE[[6]][,-1]

resu<-rbind(resu,cm2(X)[[1]])

resu<-data.frame(resu)
colnames(resu)<-col.lab
resu<-data.frame(comb=c(string,paste("{",1,",",2,",",3,",",4,",",5,",",6,"}")),resu)
resu
}
```

### Compute the ensemble scores for corpus A

```{r Calculate the F&C ensemble for Corpus A}
## Without weights
w<-c(1,1,1,1,1,1)
FEnsemb2(AdaRF.A, w)->res2
FEnsemb3(AdaRF.A, w)->res3
FEnsemb4(AdaRF.A, w)->res4
FEnsemb5(AdaRF.A, w)->res5
ensembFeature.A<-rbind(res2,res3,res4,res5)
temp<-sort.list(ensembFeature.A[,6],decreasing=TRUE)
ensembFeature.A<-data.frame(ensembFeature.A[temp,])
rownames(ensembFeature.A)<-1:dim(ensembFeature.A)[1]
write.csv(ensembFeature.A,"c:/ensemble/ensembFeature.A.csv")
corpusA[[5]]<-ensembFeature.A[1:50,6]

## Weighted ensemble for Corpus A
w<-FeaClas.A[,6]
FEnsemb2(AdaRF.A, w)->res2
FEnsemb3(AdaRF.A, w)->res3
FEnsemb4(AdaRF.A, w)->res4
FEnsemb5(AdaRF.A, w)->res5
ensembFeature.A.W<-rbind(res2,res3,res4,res5)
temp<-sort.list(ensembFeature.A.W[,6],decreasing=TRUE)
ensembFeature.A.W<-data.frame(ensembFeature.A.W[temp,])
rownames(ensembFeature.A.W)<-1:dim(ensembFeature.A.W)[1]

write.csv(ensembFeature.A.W,"c:/ensemble/ensembFeature.A.W.csv")
corpusA[[6]]<-ensembFeature.A.W[1:50,6]
kable(head(ensembFeature.A),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

```

### Compute the ensemble scores for corpus B

```{r Calculate the F&C ensemble}
## Without weights
w<-c(1,1,1,1,1,1)
FEnsemb2(AdaRF.B, w)->res2
FEnsemb3(AdaRF.B, w)->res3
FEnsemb4(AdaRF.B, w)->res4
FEnsemb5(AdaRF.B, w)->res5
ensembFeature.B<-rbind(res2,res3,res4,res5)

temp<-sort.list(ensembFeature.B[,6],decreasing=TRUE)
ensembFeature.B<-data.frame(ensembFeature.B[temp,])
rownames(ensembFeature.B)<-1:dim(ensembFeature.B)[1]
write.csv(ensembFeature.B,"c:/ensemble/ensembFeature.B.csv")
corpusB[[5]]<-ensembFeature.B[1:50,6]
kable(head(ensembFeature.B),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

## Weighted ensemble for Corpus B
w<-FeaClas.B[,6]
FEnsemb2(AdaRF.B, w)->res2
FEnsemb3(AdaRF.B, w)->res3
FEnsemb4(AdaRF.B, w)->res4
FEnsemb5(AdaRF.B, w)->res5
ensembFeature.B.W<-rbind(res2,res3,res4,res5)
temp<-sort.list(ensembFeature.B.W[,6],decreasing=TRUE)
ensembFeature.B.W<-data.frame(ensembFeature.B.W[temp,])
rownames(ensembFeature.B.W)<-1:dim(ensembFeature.B.W)[1]

write.csv(ensembFeature.B.W,"c:/ensemble/ensembFeature.B.W.csv")
kable(head(ensembFeature.B.W), format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
corpusB[[6]]<-ensembFeature.B.W[1:50,6]
```

### Draw the boxplot of F & C's and ensemble F1 scores
```{r boxplot}
#Boxplot
par(mfrow=c(1,2),cex.lab = 0.6, cex.axis = 0.6)
col=c("lightblue","gold1","pink")
lab=factor(c(rep("sin",each=6),rep("ens",each=57),rep("wes",each=57)), levels = c("sin", "ens","wes"))
#Draw boxplot of Corpus A F1 scores
F1<-c(FeaClas.A[,6],ensembFeature.A[,6],ensembFeature.A.W[,6])
FeaClas.AF1<-data.frame(lab=lab,F1=F1)
boxplot(F1 ~ lab, data = FeaClas.AF1, col=col,ylab="",xlab="");grid()
legend("bottomright", legend = c("Single-Feature", "Ensemble-Features","Wighted-Ensemble-Features"), fill = col, cex = 0.6)
#Draw boxplot of Corpus B F1 scores
F1<-c(FeaClas.B[,6],ensembFeature.B[,6],ensembFeature.B.W[,6])
FeaClas.BF1<-data.frame(lab=lab,F1=F1)
boxplot(F1 ~ lab, data = FeaClas.BF1,col=col,ylab="",xlab="");grid()
legend("bottomright", legend = c("Single-Feature", "Ensemble-Features","Wighted-Ensemble-Features"), fill = col, cex = 0.6)

```


### Integrated ensemble
### Compute method of Strom[40](ensemble for one BERT and one F & C)

```{r one BERT and one F & C}
one2one<-function(XX,YY,xw,yw)
{
resu<-numeric()
string<-c()
k=0
for(i in 1:5) 
  for(j in 1:6){
    k=k+1
    temp<-XX[[i]]
    temp[,-1]<-xw[i]*XX[[i]][,-1]+yw[j]*YY[[j]][,-1]
    resu<-rbind(resu,cm2(temp)[[1]])
    string=c(string,paste("{",B.lab[i],"|",j,"}"))
  }
 colnames(resu)<-col.lab
 resu<-data.frame(lab=string,resu)
 temp<-sort.list(resu[,6],decreasing=TRUE)
one2one.res<-resu[temp,]
one2one.res
}

#compute method of Strom40
xw<-c(1,1,1,1,1);yw<-c(1,1,1,1,1,1)
strom40A<-one2one(BERT.A,AdaRF.A,xw,yw)
corpusA[[8]]<-strom40A[,6]
head(strom40A[,6])
xw<-c(1,1,1,1,1);yw<-c(1,1,1,1,1,1)
strom40B<-one2one(BERT.B,AdaRF.B,xw,yw)
corpusB[[8]]<-strom40B[,6]
head(strom40B[,6])
```


### Computing method of Wu[39]
```{r}
Wu39<-function(XX,YY){
 #XX<-BERT.A; YY<-AdaRF.B
  Char<-(YY[[1]][,-1]+YY[[4]][,-1])/2
  Token<-(YY[[2]][,-1]+YY[[5]][,-1])/2
  Phra<-(YY[[3]][,-1]+YY[[6]][,-1])/2
  temp<-XX[[1]]
  temp[,-1]<-(XX[[1]][,-1]+XX[[2]][,-1]+XX[[3]][,-1]+
                 XX[[4]][,-1]+XX[[5]][,-1])/5

temp1<-temp; temp1[,-1]<-temp1[,-1]+Char
res1<-cm2(temp1)[[1]]
temp2<-temp; temp2[,-1]<-temp2[,-1]+Token
res2<-cm2(temp2)[[1]]
temp3<-temp; temp3[,-1]<-temp3[,-1]+Phra
res3<-cm2(temp3)[[1]]
res<-rbind(res1,res2,res3)
res<-data.frame(lab=c("{5BERTs,1,4}","{5BERTs,2,5}","{5BERTs,3,6}"),res)
res
}

Wu39.A<-Wu39(BERT.A,AdaRF.A)
corpusA[[7]]<-Wu39.A[,6]
summary(Wu39.A[,6])


Wu39.B<-Wu39(BERT.B,AdaRF.B)
corpusB[[7]]<-Wu39.B[,6]
summary(Wu39.B[,6])

```


### Integrated ensemble
```{r }
interEnsemb<-function(BB,FF,wb,wf){
eBA.lab<-list()
comb2<-combn(1:5, 2);L2<-dim(comb2)[2]
comb3<-combn(1:5, 3);L3<-dim(comb3)[2]
comb4<-combn(1:5, 4);L4<-dim(comb4)[2]
comb5<-combn(1:5, 5)

# Set the label list for the BERTs combination
for(i in 1:L2) eBA.lab[[i]]<-comb2[,i]
for(i in 1:L3) {(L2+i)->k; eBA.lab[[k]]<-comb3[,i]}
for(i in 1:L4) {(L2+L3+i)->k; eBA.lab[[k]]<-comb4[,i]}
eBA.lab[[L2+L3+L4+1]]<-comb5[,1]

# Set the label list for the F & C combination
eFA.lab<-list()
comb2<-combn(1:6, 2);L2<-dim(comb2)[2]
comb3<-combn(1:6, 3);L3<-dim(comb3)[2]
comb4<-combn(1:6, 4);L4<-dim(comb4)[2]
comb5<-combn(1:6, 5);L5<-dim(comb5)[2]

for(i in 1:L2) eFA.lab[[i]]<-comb2[,i]
for(i in 1:L3) {(L2+i)->k; eFA.lab[[k]]<-comb3[,i]}
for(i in 1:L4) {(L2+L3+i)->k; eFA.lab[[k]]<-comb4[,i]}
for(i in 1:L5) {(L2+L3+L4+i)->k; eFA.lab[[k]]<-comb5[,i]}
eFA.lab[[L2+L3+L4+L5+1]]<-c(1,2,3,4,5,6)

#Compute for all combinations
resu<-c()
resLab<-c()
for(i in 1:length(eBA.lab)){
  for(j in 1:length(eFA.lab)){
    #Data creation for BERTs
    
    tempBi<-eBA.lab[[i]]
    LBi<-length(tempBi)
    BX<-BB[[tempBi[1]]];
    for(k in 2:LBi)
      BX[,-1]<-BX[,-1]*wb[tempBi[1]]+wb[tempBi[k]]*BB[[tempBi[k]]][,-1]
    BX[,-1]<-BX[,-1]/5
    
    #Data creation for F & C
    tempFj<-eFA.lab[[j]]
    LFj<-length(tempFj)
    FX<-FF[[tempFj[1]]]
    for(k in 2:LFj)
      FX[,-1]<-FX[,-1]*wf[tempFj[1]]+wf[tempFj[k]]*FF[[tempFj[k]]][,-1]
    FX[,-1]<-FX[,-1]/6
    
     #Integrative Ensemble
    BFX<-BX; BFX[,-1]<-BX[,-1]+FX[,-1]
   
    labi<- paste(B.lab[eBA.lab[[i]]], collapse = ",")
    labj<- paste(eFA.lab[[j]], collapse = ",")
    labij<-paste("{",labi,"|",labj,"}")
    resLab<-rbind(resLab,labij)
    resu<-rbind(resu,cm2(BFX)[[1]])
  }
}
resu<-data.frame(resLab, resu)
temp<-sort.list(resu[,6],decreasing = TRUE)
resu<-resu[temp,]
rownames(resu)<-1:dim(resu)[1]
colnames(resu)<-c("lab",col.lab)
resu
}
```

### Compute the integrative ensemble for corpus A
```{r }
#without weight
wb<-c(1,1,1,1,1); wf<-c(1,1,1,1,1,1)
interEnsemb(BERT.A,AdaRF.A, wb,wf)->InterEnsemble.A
temp<-sort.list(InterEnsemble.A[,6],decreasing = TRUE)
InterEnsemble.A<-InterEnsemble.A[temp,]
write.csv(InterEnsemble.A,"c:/ensemble/InterEnsemble.A.csv")
corpusA[[9]]<-InterEnsemble.A[1:50,6]
kable(head(InterEnsemble.A,10),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

#Weighted ensemble
wb<-singBERT.A[,6]
wf<-FeaClas.A[,6]
interEnsemb(BERT.A,AdaRF.A, wb,wf)->InterEnsemble.A.W
temp<-sort.list(InterEnsemble.A.W[,6],decreasing = TRUE)
InterEnsemble.A.W<-InterEnsemble.A.W[temp,]
write.csv(InterEnsemble.A.W,"c:/ensemble/InterEnsemble.A.W.csv")
corpusA[[10]]<-InterEnsemble.A.W[1:50,6]

kable(head(InterEnsemble.A.W),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
```

### Compute the integrative ensemble for corpus B
```{r ensemble for corpus B}
#Without weight
wb<-c(1,1,1,1,1);wf<-c(1,1,1,1,1,1)
interEnsemb(BERT.B,AdaRF.B, wb,wf)->InterEnsemb.B
temp<-sort.list(InterEnsemb.B[,6],decreasing = TRUE)
InterEnsemble.B<-InterEnsemb.B[temp,]
corpusB[[9]]<-InterEnsemb.B[1:50,6]
write.csv(InterEnsemb.B,"C:/ensemble/InterEnsemb.B.csv")
kable(head(InterEnsemb.B,10),format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")
#Weighted ensemble
wb<-singBERT.B[,6]; wf<-FeaClas.B[,6]
interEnsemb(BERT.B,AdaRF.B, wb,wf)->InterEnsemb.B.W
temp<-sort.list(InterEnsemb.B.W[,6],decreasing = TRUE)
InterEnsemble.A.W<-InterEnsemb.B.W[temp,]
corpusB[[10]]<-InterEnsemb.B.W[1:50,6]
write.csv(InterEnsemb.B.W,"c:/ensemble/InterEnsemb.B.W.csv")

```
### Create table 4
```{r create table 4}
max_vector1<-numeric()
mean_vector1<-numeric()
max_vector2<-numeric()
mean_vector2<-numeric()
sd_vector1<-numeric()
sd_vector2<-numeric()
for(i in 1:10){
  max_vector1<-c(max_vector1,max(corpusA[[i]]))
  max_vector2<-c(max_vector2,max(corpusB[[i]]))
  mean_vector1<-c(mean_vector1,mean(corpusA[[i]]))
  mean_vector2<-c(mean_vector2,mean(corpusB[[i]]))
  sd_vector1<-c(sd_vector1,sd(corpusA[[i]]))
  sd_vector2<-c(sd_vector2,sd(corpusB[[i]]))
}
# Set data name
labs<-c("BERTs",
        "Ensemble BERTs", 
        "Weighted Ensemble BERTs",
        "Feature",
        "Ensemble Features & Classifiers",
        "Weighted Ensemble Features & Classifiers",
        "Ensemble One Feature & Classifiers and BERTs [39]",
        "Ensemble One BETR and Features & Classifiers [40]",
        "Intergreted Ensemble",
        "Intergreted Weighted Ensemble"
    )

table4<-data.frame(method=labs,
mean=mean_vector1,sd=sd_vector1,Max=max_vector1,
mean=mean_vector2,sd=sd_vector2,Max=max_vector2
)

table4[,-1]<-round(table4[,-1],3)
write.csv(table4,"C:/ensemble/table4.csv")
kable(table4,format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

```

### Create table 5
```{r Create table 5}
table5A<-data.frame(
  comBERT=ensemBERT.A[1:10,1],cB_F1=round(ensemBERT.A[1:10,6],3),
  comFea=ensembFeature.A[1:10,1],cF_F1=round(ensembFeature.A[1:10,6],3),
  intEns=InterEnsemble.A[1:10,1],cF_F1=round(InterEnsemble.A[1:10,6],3)
  
                    )
kable(table5A,format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

table5B<-data.frame(
  comBERT=ensemBERT.B[1:10,1],cB_F1=round(ensemBERT.B[1:10,6],3),
  comFea=ensembFeature.B[1:10,1],cF_F1=round(ensembFeature.B[1:10,6],3),
  intEns=InterEnsemble.B[1:10,1],cF_F1=round(InterEnsemble.B[1:10,6],3)
  )
kable(table5B,format = "html") %>% 
  kable_styling(full_width = FALSE, position = "left")

table5<-rbind(table5A,table5B)
#kable(table5, format = "html") %>% 
#  kable_styling(full_width = FALSE, position = "left")
write.csv(table5,"c:/ensemble/table5.csv")
```

### Draw Figure 2
#### For Corpus A
```{r fig.width=12, fig.height=6}
names(corpusA)<-labs
# Set horizontal axis labels
x_labels <- LETTERS[1:10]

# Set legend label
legend_labels <- paste(x_labels, names(corpusA), sep = ": ")

# Draw Box-plot of Corpus A
par(mfrow=c(1,2),cex.lab = 0.6, cex.axis = 0.6,
  mgp = c(1, 0.4, 0),mai = c(1, 1, 1, 1)) 
  boxplot(corpusA, col = c("lightblue"),names = x_labels, main = "", xlab = "Corpus A", ylab = "F1 Scor", cex.axis = 0.6, cex.lab = 0.6)

# Add grid lines and legend
grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted")
legend("bottomright", legend = legend_labels, title = "Dataset Names", cex = 0.6)

# Draw Box-plot of Corpus B
# Set data name
names(corpusB)<-labs
# Set horizontal axis labels
x_labels <- LETTERS[1:10]

# Set legend label
legend_labels <- paste(x_labels, names(corpusB), sep = ": ")

# Draw Box-plot of Corpus B
par(mgp = c(1, 0.4, 0),mai = c(1, 1, 1, 1)) 
boxplot(corpusB, col = "lightgreen",names = x_labels, main = "", xlab = "Corpus B", ylab = "F1 Scor", cex.axis = 0.6, cex.lab = 0.6)

# Add grid lines and legend
grid(nx = NULL, ny = NULL, col = "lightgray", lty = "dotted")
legend("bottomright", legend = legend_labels, title = "Dataset Names", cex = 0.5)

```
